---
title: "MA615-Final-Project"
author: "Fengyuan Shen (Vincent)"
date: "Dec 15 2023"
format: html
editor: visual
---

## Abstract

## Introduction

```{r echo=FALSE}
library(tidyverse)
library(shiny)
library(leaflet)
library(leaflet.extras)
```

## General description

### Map of the island state

micronesia一共有四个state: Chuuk Kosrae Pohnpei Yap, 可以做一个下拉菜单显示他们

#### Pohnpei

```{r}
# Set the coordinates
micronesia_Pohnpei <- c(6.8874, 158.2150)

# Create map
micronesia_Pohnpei_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1], 
             popup = "State: Pohnpei<br>State Capital: Kolonia<br>Administrative Capital: Palikir") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1],
                      label = "State: Pohnpei, Administrative Capital: Palikir",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-100, -10)))

micronesia_Pohnpei_map
```

#### Chuuk

```{r}
# Set the coordinates
micronesia_Chuuk <- c(7.4500, 151.8500)

# Create map
micronesia_Chuuk_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], 
             popup = "State: Chuuk<br>Capital: Weno") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1],
                      label = "State: Chuuk, Capital: Weno",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-20, 0)))

micronesia_Chuuk_map
```

#### Kosrae

```{r}
# Set the coordinates
micronesia_Kosrae <- c(5.3258, 163.0086)

# Create map
micronesia_Kosrae_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1], 
             popup = "State: Kosrae<br>Capital: Tofol") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1],
                      label = "State: Kosrae, Capital: Tofol",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'right',
                                                  offset = c(40, -10)))

micronesia_Kosrae_map
```

#### Yap

```{r}
# Set the coordinates
micronesia_Yap <- c(9.5167, 138.1333)

# Create map
micronesia_Yap_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Yap[2], lat = micronesia_Yap[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Yap[2], lat = micronesia_Yap[1], 
             popup = "State: Yap<br>Capital: Colonia") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Yap[2], lat = micronesia_Yap[1],
                      label = "State: Yap, Capital: Colonia",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-90, -10)))

micronesia_Yap_map
```

Palikir is the capital city of the Federated States of Micronesia located in the western Pacific Ocean. A town of slightly under 5,000 residents, it is part of the larger Sokehs municipality, which had a population of 6,647 as of 2010, out of the nation's total population of 106,487. It is situated on the northwest side of Pohnpei island (population 34,789), a high volcanic island surrounded by a fringing coral reef. Nearby to the northeast is the island's largest settlement, the coastal town of Kolonia. It was declared the capital of Micronesia in 1989.

### Map showing the location of the island state in the world

```{r}
# Set the coordinates
micronesia_Pohnpei <- c(6.8874, 158.2150)
micronesia_Chuuk <- c(7.4500, 151.8500)
micronesia_Kosrae <- c(5.3258, 163.0086)
micronesia_Yap <- c(9.5167, 138.1333)

# Create map
micronesia_map_world <- leaflet() |> 
  addProviderTiles(providers$Esri.NatGeoWorldMap) |> 
  setView(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], zoom = 3) |> 
  addCircles(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1],
             radius = 650000, color = '#D90429', fillColor = '#D90429',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Pohnpei") %>%
  addCircles(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1],
             radius = 550000, color = '#134074', fillColor = '#134074',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Chuuk") %>%
  addCircles(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1],
             radius = 450000, color = '#386641', fillColor = '#386641',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Kosrae") %>%
  addCircles(lng = micronesia_Yap[2], lat = micronesia_Yap[1],
             radius = 500000, color = '#F9C80E', fillColor = '#F9C80E',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Yap")

micronesia_map_world
```

### Key facts about the island state

### A brief narrative description of the island state

## Key demographics

## Comparison of the Island State relative to other island states in the same region

## SWOT analysis of the Island State

## Reference

### **1. 岛屿国家的一般描述**

-   **地图展示**：

    -   使用R的**`ggplot2`**包或**`leaflet`**包来创建密克罗尼西亚的地图。

    -   展示密克罗尼西亚在世界地图上的位置，可以使用**`maps`**包。

-   **关键事实和描述**：

    -   通过研究，整理关于密克罗尼西亚的基本信息，如历史、地理、文化等。

    -   可以在一张图表里绘制所有数据，然后画一个可以设置年份的轴

### **2. 关键人口统计信息**

-   收集并展示关于人口规模、人口密度、城市化程度等数据。

-   可以使用图表来呈现这些数据，例如用**`ggplot2`**创建条形图或饼图。

### **3. 与同一地区的其他岛屿国家比较**

-   选择几个与密克罗尼西亚地理或经济条件相似的岛屿国家进行比较。
-   **数据比较**：
    -   收集有关这些岛屿的相似数据，如GDP、教育水平、医疗设施等。

    -   使用R创建比较图表，如散点图或直方图。

### **4. SWOT分析**

-   **分析密克罗尼西亚的优势、劣势、机会和威胁**：

    -   研究经济、环境、政治等方面。

    -   这部分可能更多是叙述性的，但可以通过图表或图像来辅助展示。
