---
title: "MA615-Final-Project"
author: "Fengyuan Shen (Vincent)"
date: "Dec 15 2023"
format: html
editor: visual
---

## Introduction

这里加一些Micronesia的图片（比如国旗），按照老头的要求

这里是综述，比如国土面积，人口，语言，有几个州，人类发展指数之类的信息

```{r echo=FALSE}
library(tidyverse)
library(ggplot2)
library(shiny)
library(leaflet)
library(leaflet.extras)
library(treemap)
```

```{r}
# Read the CSV file and skip the first 4 lines
micronesia_data <- read_csv("data/API_FSM_DS2_en_csv_v2_6235080.csv", skip = 4)
```

## General description

### Map of the island state

#### Pohnpei

```{r}
# Set the coordinates
micronesia_Pohnpei <- c(6.8874, 158.2150)

# Create map
micronesia_Pohnpei_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1], 
             popup = "State: Pohnpei<br>State Capital: Kolonia<br>Administrative Capital: Palikir") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1],
                      label = "State: Pohnpei, Administrative Capital: Palikir",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-100, -10)))

micronesia_Pohnpei_map
```

#### Chuuk

```{r}
# Set the coordinates
micronesia_Chuuk <- c(7.4500, 151.8500)

# Create map
micronesia_Chuuk_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], 
             popup = "State: Chuuk<br>Capital: Weno") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1],
                      label = "State: Chuuk, Capital: Weno",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-20, 0)))

micronesia_Chuuk_map
```

#### Kosrae

```{r}
# Set the coordinates
micronesia_Kosrae <- c(5.3258, 163.0086)

# Create map
micronesia_Kosrae_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1], 
             popup = "State: Kosrae<br>Capital: Tofol") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1],
                      label = "State: Kosrae, Capital: Tofol",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'right',
                                                  offset = c(40, -10)))

micronesia_Kosrae_map
```

#### Yap

```{r}
# Set the coordinates
micronesia_Yap <- c(9.5167, 138.1333)

# Create map
micronesia_Yap_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Yap[2], lat = micronesia_Yap[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Yap[2], lat = micronesia_Yap[1], 
             popup = "State: Yap<br>Capital: Colonia") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Yap[2], lat = micronesia_Yap[1],
                      label = "State: Yap, Capital: Colonia",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-90, -10)))

micronesia_Yap_map
```

Palikir is the capital city of the Federated States of Micronesia located in the western Pacific Ocean. A town of slightly under 5,000 residents, it is part of the larger Sokehs municipality, which had a population of 6,647 as of 2010, out of the nation's total population of 106,487. It is situated on the northwest side of Pohnpei island (population 34,789), a high volcanic island surrounded by a fringing coral reef. Nearby to the northeast is the island's largest settlement, the coastal town of Kolonia. It was declared the capital of Micronesia in 1989.

### World Map Highlighting the Island State's Location

```{r}
# Set the coordinates
micronesia_Pohnpei <- c(6.8874, 158.2150)
micronesia_Chuuk <- c(7.4500, 151.8500)
micronesia_Kosrae <- c(5.3258, 163.0086)
micronesia_Yap <- c(9.5167, 138.1333)

# Create map
micronesia_map_world <- leaflet() |> 
  addProviderTiles(providers$Esri.NatGeoWorldMap) |> 
  setView(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], zoom = 3) |> 
  addCircles(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1],
             radius = 650000, color = '#D90429', fillColor = '#D90429',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Pohnpei") |> 
  addCircles(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1],
             radius = 550000, color = '#134074', fillColor = '#134074',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Chuuk") |> 
  addCircles(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1],
             radius = 450000, color = '#386641', fillColor = '#386641',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Kosrae") |> 
  addCircles(lng = micronesia_Yap[2], lat = micronesia_Yap[1],
             radius = 500000, color = '#F9C80E', fillColor = '#F9C80E',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Yap")

micronesia_map_world
```

### Economic Characteristics of the Island State

```{r}
# A list of selected indicators
selected_indicators <- c('GDP (current US$)', 'GDP growth (annual %)', 
                         'GDP per capita (current US$)', 
                         'GDP per capita growth (annual %)',
                         'Imports of goods and services (current US$)', 
                         'Exports of goods and services (current US$)', 
                         'Population, total', 'Population growth (annual %)', 
                         'Travel services (% of commercial service exports)',
                         'Population, female (% of total population)',
                         'Population, male (% of total population)',
                         'Life expectancy at birth, total (years)')

# Filter data
filtered_data <- micronesia_data |> 
                 filter(`Indicator Name` %in% selected_indicators) |> 
                 select(-c(`Country Name`, `Country Code`, `Indicator Code`))

# Convert data to long format
long_data <- filtered_data |> 
             pivot_longer(cols = `1986`:`2022`, names_to = "Year", values_to = "Value") |> 
             mutate(Year = as.numeric(Year))  # Convert year to numeric
```

#### GDP

```{r}
gdp_growth_data <- long_data |> 
                   filter(`Indicator Name` %in% c('GDP (current US$)', 
                                                  'GDP growth (annual %)'))

ggplot(data = gdp_growth_data, aes(x = Year)) +
    geom_col(data = filter(gdp_growth_data, `Indicator Name` == 'GDP (current US$)'),
             aes(y = Value / 10^6, fill = Value), color = "black") +
    scale_fill_gradientn(colours = c("#03045E", "#012A4A", "#013A63", "#023E8A",
                                     "#014F86", "#277DA1", "#577590", "#4D908E", 
                                     "#43AA8B", "#90BE6D", "#F9C74F", "#F9844A",
                                     "#DC2F02", "#D00000"),
                       values = seq(0, 1, length.out = 14)) +
    # Amplify the GDP growth rate to match the size of GDP
    geom_line(data = filter(gdp_growth_data, `Indicator Name` == 'GDP growth (annual %)'), 
              aes(y = Value * 10 + 300), color = "#FFC300", linewidth = 1, group = 1) + 
    scale_y_continuous(sec.axis = sec_axis(~./10 - 30, 
                                           name = "GDP Growth Rate (annual %)")) +
    labs(
      title = "GDP and GDP Growth Rate Over Time", 
      x = "Year", y = "GDP (million current US$)"
      ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "none"
      )
```

#### GDP Per Capita

```{r}
gdp_per_capita_data <- long_data |> 
                      filter(`Indicator Name` %in% c('GDP per capita (current US$)', 
                                                     'GDP per capita growth (annual %)'))

ggplot(data = gdp_per_capita_data, aes(x = Year)) +
    geom_col(data = filter(gdp_per_capita_data, 
                           `Indicator Name` == 'GDP per capita (current US$)'),
             aes(y = Value, fill = Value), color = "black") +
    scale_fill_gradientn(colours = c("#03045E", "#012A4A", "#013A63", "#023E8A",
                                     "#014F86", "#277DA1", "#577590", "#4D908E", 
                                     "#43AA8B", "#90BE6D", "#F9C74F", "#F9844A",
                                     "#DC2F02", "#D00000"),
                       values = seq(0, 1, length.out = 14)) +
    geom_line(data = filter(gdp_per_capita_data, 
                            `Indicator Name` == 'GDP per capita growth (annual %)'), 
              aes(y = Value * 100 + 2500), color = "#FFC300", linewidth = 1, group = 1) + 
    scale_y_continuous(sec.axis = sec_axis(~./100 - 25, name = 
                                             "GDP Per Capita Growth Rate (annual %)")) +
    labs(
      title = "GDP Per Capita and its Growth Rate Over Time", 
      x = "Year", y = "GDP Per Capita (current US$)"
      ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "none"
      )
```

#### Export and Import

```{r}
trade_data <- long_data |> 
              filter(`Indicator Name` %in% c('Imports of goods and services (current US$)',
                                             'Exports of goods and services (current US$)'))

ggplot(trade_data, aes(x = Year, y = Value / 10^6, fill = `Indicator Name`)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_fill_manual(values = c('Imports of goods and services (current US$)' = '#003566',
                                 'Exports of goods and services (current US$)' = '#D62828'),
                      name = "Trade Type", labels = c("Imports", "Exports")) +
    labs(
      title = "Imports and Exports Over Time", 
      x = "Year", y = "Value (million current US$)"
      ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1)
      )
```

### Overview of Political, Social, Cultural, and Environmental Aspects

可以用Wikipedia的描述性语言，分类别描述

## Key Demographics

### Population and its Growth Rate

```{r}
population_data <- long_data |> 
                   filter(`Indicator Name` %in% c('Population, total', 
                                                  'Population growth (annual %)'))

ggplot(data = population_data, aes(x = Year)) +
    geom_col(data = filter(population_data, `Indicator Name` == 'Population, total'), 
             aes(y = Value / 1000, fill = Value), color = "black") +
    scale_fill_gradientn(colours = c("#D00000", "#DC2F02", "#F3722C", "#F9844A",
                                     "#F9C74F", "#FFE347", "#90BE6D", "#4D908E",
                                     "#43AA8B", "#006F57", "#277DA1", "#014F86"),
                       values = seq(0, 1, length.out = 15)) +
    geom_line(data = filter(population_data, 
                            `Indicator Name` == 'Population growth (annual %)'), 
              aes(y = Value * 10 + 90), color = "#FFC300", linewidth = 1, group = 1) +
    scale_y_continuous(sec.axis = sec_axis(~./10 - 9, 
                                           name = "Population Growth Rate (annual %)")) +
    labs(
      title = "Population and Population Growth Rate Over Time", 
      x = "Year", y = "Total Population (thousand)"
      ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "none"
      )
```

### Demographic Composition

The indigenous population of the nation, which is predominantly [Micronesian](https://en.wikipedia.org/wiki/Micronesians "Micronesians"), consists of various ethnolinguistic groups. It has a nearly 100% Pacific Islander and [Asian](https://en.wikipedia.org/wiki/Asian_people "Asian people") population: [Chuukese](https://en.wikipedia.org/wiki/Chuukese_people "Chuukese people") 48.8%, [Pohnpeian](https://en.wikipedia.org/wiki/Pohnpeian_language "Pohnpeian language") 24.2%, [Kosraean](https://en.wikipedia.org/wiki/Kosraean_language "Kosraean language") 6.2%, [Yapese](https://en.wikipedia.org/wiki/Yapese_people "Yapese people") 5.2%, [Yap](https://en.wikipedia.org/wiki/Yap "Yap") outer islands 4.5%, [Asian](https://en.wikipedia.org/wiki/Asian_ethnic_groups "Asian ethnic groups") 1.8%, [Polynesian](https://en.wikipedia.org/wiki/Polynesians "Polynesians") 1.5%, other 6.4%, unknown 1.4%. 这个用树形图

```{r}
# 创建人口构成的数据框
composition_data <- data.frame(
  Group = c("Chuukese", "Pohnpeian", "Kosraean", "Yapese", 
            "Yap outer islands", "Asian", "Polynesian", "Other", "Unknown"),
  Percentage = c(48.8, 24.2, 6.2, 5.2, 4.5, 1.8, 1.5, 6.4, 1.4)
)

# 绘制树形图
treemap(
  composition_data,
  index = "Group",
  vSize = "Percentage",
  title = "Population Composition",
  fontsize.labels = c(12, 10, 8),
  fontcolor.labels = c("white", "white", "white"),
  fontface.labels = c("bold", "bold", "bold"),
  align.labels = list(
    c("center", "center"),
    c("left", "top"),
    c("left", "bottom")
  ),
  overlap.labels = 0.5,
  inflate.labels = F
)
```

### Male vs Female

```{r}
proportion_data <- long_data |> 
                   filter(`Indicator Name` %in% c('Population, female (% of total population)', 'Population, male (% of total population)'))

ggplot(proportion_data, aes(x = Year, y = Value , fill = `Indicator Name`)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_fill_manual(values = c('Population, male (% of total population)' = '#003566',
                                 'Population, female (% of total population)' = '#D62828'),
                      name = "Gender", labels = c("Male Proportion", "Female Proportion")) +
    labs(
      title = "Male and Female Population Proportion",
      x = "Year", y = "Population Proportion (%)") +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1)
      )
```

### Life expectancy

```{r}
life_expectancy_data <- long_data |> 
                   filter(`Indicator Name` %in% 'Life expectancy at birth, total (years)')

ggplot(life_expectancy_data, aes(x = Year, y = Value)) +
  geom_line(color = "#006F57", linewidth = 1) +
  geom_point(color = "#CD1624", size = 2) +
  labs(title = "Life Expectancy at Birth", 
       y = "Life Expectancy (Years)", 
       x = "Year") +
  theme_minimal() +
  theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1)
      )
```

## Comparison with Other Regional Island States

随便找几个周边的国家，然后对比GDP，人均GDP，人口，预期寿命，HDI（UNData选一些指标）

用UnData网站里Micronesia区域的国家（选4个）来作对比

这里使用table和graphs来展示

## SWOT Analysis

## Reference

### **4. SWOT分析**

-   **分析密克罗尼西亚的优势、劣势、机会和威胁**：

    -   研究经济、环境、政治等方面。比如进出口额占据GDP的比重

    -   这部分可能更多是叙述性的，但可以通过图表或图像来辅助展示。
