---
title: "MA615-Final-Project"
author: "Fengyuan Shen (Vincent)"
date: "Dec 15 2023"
format: html
editor: visual
---

## Introduction

The Federated States of Micronesia (FSM), also known as Micronesia, is an island country in the Pacific Ocean's Micronesia subregion. It consists of four states - Yap, Chuuk, Pohnpei, and Kosrae - spanning about 607 islands across 2,700 km near the equator. These islands are situated northeast of Indonesia and Papua New Guinea, and south of Guam. Although the FSM's land area is only about 702 km², its marine territory covers nearly 3 million km², ranking it 14th in the world for its exclusive economic zone.

Palikir on Pohnpei Island is the capital, while Weno in Chuuk is the largest city. Each state centers around volcanic islands, with many outlying atolls, especially in the Caroline Islands region. The term 'Micronesia' often refers to either the FSM or the broader region comprising several countries.

Formerly under U.S. administration as part of the Trust Territory of the Pacific Islands, FSM gained sovereignty on November 3, 1986, through a Compact of Free Association with the U.S., after establishing its constitution on May 10, 1979. It's a United Nations member and part of the Pacific Community since 1983.

```{r echo=FALSE}
library(tidyverse)
library(ggplot2)
library(shiny)
library(leaflet)
library(leaflet.extras)
library(treemap)
library(treemapify)
library(gt)
library(gtExtras)
```

```{r}
# Read the CSV file and skip the first 4 lines
micronesia_data <- read_csv("data/API_FSM_DS2_en_csv_v2_6235080.csv", skip = 4)
```

## General Description

### Map of the Island State

#### Pohnpei

```{r}
# Set the coordinates
micronesia_Pohnpei <- c(6.8874, 158.2150)

# Create map
micronesia_Pohnpei_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1], 
             popup = "State: Pohnpei<br>State Capital: Kolonia<br>Administrative Capital: Palikir") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1],
                      label = "State: Pohnpei, Administrative Capital: Palikir",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-100, -10)))

micronesia_Pohnpei_map
```

#### Chuuk

```{r}
# Set the coordinates
micronesia_Chuuk <- c(7.4500, 151.8500)

# Create map
micronesia_Chuuk_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], 
             popup = "State: Chuuk<br>Capital: Weno") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1],
                      label = "State: Chuuk, Capital: Weno",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-20, 0)))

micronesia_Chuuk_map
```

#### Kosrae

```{r}
# Set the coordinates
micronesia_Kosrae <- c(5.3258, 163.0086)

# Create map
micronesia_Kosrae_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1], 
             popup = "State: Kosrae<br>Capital: Tofol") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1],
                      label = "State: Kosrae, Capital: Tofol",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'right',
                                                  offset = c(40, -10)))

micronesia_Kosrae_map
```

#### Yap

```{r}
# Set the coordinates
micronesia_Yap <- c(9.5167, 138.1333)

# Create map
micronesia_Yap_map <- leaflet() |>
  # Add base layer
  addProviderTiles(providers$OpenStreetMap) |> 
  # Set the view and zoom level
  setView(lng = micronesia_Yap[2], lat = micronesia_Yap[1], zoom = 11) |>
  # Add a marker with a popup
  addMarkers(lng = micronesia_Yap[2], lat = micronesia_Yap[1], 
             popup = "State: Yap<br>Capital: Colonia") |> 
  # Add a label marker
  addLabelOnlyMarkers(lng = micronesia_Yap[2], lat = micronesia_Yap[1],
                      label = "State: Yap, Capital: Colonia",
                      labelOptions = labelOptions(noHide = TRUE,
                                                  direction = 'auto',
                                                  offset = c(-90, -10)))

micronesia_Yap_map
```

Palikir is the capital city of the Federated States of Micronesia located in the western Pacific Ocean. A town of slightly under 5,000 residents, it is part of the larger Sokehs municipality, which had a population of 6,647 as of 2010, out of the nation's total population of 106,487. It is situated on the northwest side of Pohnpei island (population 34,789), a high volcanic island surrounded by a fringing coral reef. Nearby to the northeast is the island's largest settlement, the coastal town of Kolonia. It was declared the capital of Micronesia in 1989.

### World Map Highlighting the Island State's Location

```{r}
# Set the coordinates
micronesia_Pohnpei <- c(6.8874, 158.2150)
micronesia_Chuuk <- c(7.4500, 151.8500)
micronesia_Kosrae <- c(5.3258, 163.0086)
micronesia_Yap <- c(9.5167, 138.1333)

# Create map
micronesia_map_world <- leaflet() |> 
  addProviderTiles(providers$Esri.NatGeoWorldMap) |> 
  setView(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1], zoom = 3) |> 
  addCircles(lng = micronesia_Pohnpei[2], lat = micronesia_Pohnpei[1],
             radius = 650000, color = '#D90429', fillColor = '#D90429',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Pohnpei") |> 
  addCircles(lng = micronesia_Chuuk[2], lat = micronesia_Chuuk[1],
             radius = 550000, color = '#134074', fillColor = '#134074',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Chuuk") |> 
  addCircles(lng = micronesia_Kosrae[2], lat = micronesia_Kosrae[1],
             radius = 450000, color = '#386641', fillColor = '#386641',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Kosrae") |> 
  addCircles(lng = micronesia_Yap[2], lat = micronesia_Yap[1],
             radius = 500000, color = '#F9C80E', fillColor = '#F9C80E',
             fillOpacity = 0.7, weight = 2, dashArray = '5, 5',
             popup = "Yap")

micronesia_map_world
```

### Economic Characteristics of the Island State

```{r}
# A list of selected indicators
selected_indicators <- c('GDP (current US$)', 'GDP growth (annual %)', 
                         'GDP per capita (current US$)', 
                         'GDP per capita growth (annual %)',
                         'Imports of goods and services (current US$)', 
                         'Exports of goods and services (current US$)', 
                         'Population, total', 'Population growth (annual %)', 
                         'Travel services (% of commercial service exports)',
                         'Population, female (% of total population)',
                         'Population, male (% of total population)',
                         'Life expectancy at birth, total (years)')

# Filter data
filtered_data <- micronesia_data |> 
                 filter(`Indicator Name` %in% selected_indicators) |> 
                 select(-c(`Country Name`, `Country Code`, `Indicator Code`))

# Convert data to long format
long_data <- filtered_data |> 
             pivot_longer(cols = `1986`:`2022`, names_to = "Year", values_to = "Value") |> 
             mutate(Year = as.numeric(Year))  # Convert year to numeric
```

#### GDP

```{r}
gdp_growth_data <- long_data |> 
                   filter(`Indicator Name` %in% c('GDP (current US$)', 
                                                  'GDP growth (annual %)'))

ggplot(data = gdp_growth_data, aes(x = Year)) +
    geom_col(data = filter(gdp_growth_data, `Indicator Name` == 'GDP (current US$)'),
             aes(y = Value / 10^6, fill = Value), color = "black") +
    scale_fill_gradientn(colours = c("#03045E", "#012A4A", "#013A63", "#023E8A",
                                     "#014F86", "#277DA1", "#577590", "#4D908E", 
                                     "#43AA8B", "#90BE6D", "#F9C74F", "#F9844A",
                                     "#DC2F02", "#D00000"),
                       values = seq(0, 1, length.out = 14)) +
    # Amplify the GDP growth rate to match the size of GDP
    geom_line(data = filter(gdp_growth_data, `Indicator Name` == 'GDP growth (annual %)'), 
              aes(y = Value * 10 + 300), color = "#FFC300", linewidth = 1, group = 1) + 
    scale_y_continuous(sec.axis = sec_axis(~./10 - 30, 
                                           name = "GDP Growth Rate (annual %)")) +
    labs(
      title = "GDP and GDP Growth Rate Over Time", 
      x = "Year", y = "GDP (million current US$)"
      ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "none"
      )
```

#### GDP Per Capita

```{r}
gdp_per_capita_data <- long_data |> 
                      filter(`Indicator Name` %in% c('GDP per capita (current US$)', 
                                                     'GDP per capita growth (annual %)'))

ggplot(data = gdp_per_capita_data, aes(x = Year)) +
    geom_col(data = filter(gdp_per_capita_data, 
                           `Indicator Name` == 'GDP per capita (current US$)'),
             aes(y = Value, fill = Value), color = "black") +
    scale_fill_gradientn(colours = c("#03045E", "#012A4A", "#013A63", "#023E8A",
                                     "#014F86", "#277DA1", "#577590", "#4D908E", 
                                     "#43AA8B", "#90BE6D", "#F9C74F", "#F9844A",
                                     "#DC2F02", "#D00000"),
                       values = seq(0, 1, length.out = 14)) +
    geom_line(data = filter(gdp_per_capita_data, 
                            `Indicator Name` == 'GDP per capita growth (annual %)'), 
              aes(y = Value * 100 + 2500), color = "#FFC300", linewidth = 1, group = 1) + 
    scale_y_continuous(sec.axis = sec_axis(~./100 - 25, name = 
                                             "GDP Per Capita Growth Rate (annual %)")) +
    labs(
      title = "GDP Per Capita and its Growth Rate Over Time", 
      x = "Year", y = "GDP Per Capita (current US$)"
      ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "none"
      )
```

#### Export and Import

```{r}
trade_data <- long_data |> 
              filter(`Indicator Name` %in% c('Imports of goods and services (current US$)',
                                             'Exports of goods and services (current US$)'))

ggplot(trade_data, aes(x = Year, y = Value / 10^6, fill = `Indicator Name`)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_fill_manual(values = c('Imports of goods and services (current US$)' = '#003566',
                                 'Exports of goods and services (current US$)' = '#D62828'),
                      name = "Trade Type", labels = c("Imports", "Exports")) +
    labs(
      title = "Imports and Exports Over Time", 
      x = "Year", y = "Value (million current US$)"
      ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1)
      )
```

### Overview of Political, Social, Cultural, and Other Aspects

**Politics**: Gained independence from US-administered Trust Territory of the Pacific Islands in 1986. It's a democratic nation with a Compact of Free Association with the United States.

**Economy**: Relies on subsistence farming, fishing, and US financial aid. Limited natural resources; potential for tourism development is hindered by remoteness.

**History**: Inhabited for over 4,000 years; influenced by Spanish, German, and Japanese rule. Significant World War II site.

**Population and Culture**: Predominantly Micronesian population, with diverse ethnolinguistic groups. Rich in traditions and customs, with notable sites like Yap's Rai stones and Pohnpei's Nan Madol ruins.

**Environment**: Tropical rainforest climate, characterized by high rainfall, lush landscapes, and unique ecosystems.

## Key Demographics

### Population and its Growth Rate

```{r}
population_data <- long_data |> 
                   filter(`Indicator Name` %in% c('Population, total', 
                                                  'Population growth (annual %)'))

ggplot(data = population_data, aes(x = Year)) +
    geom_col(data = filter(population_data, `Indicator Name` == 'Population, total'), 
             aes(y = Value / 1000, fill = Value), color = "black") +
    scale_fill_gradientn(colours = c("#D00000", "#DC2F02", "#F3722C", "#F9844A",
                                     "#F9C74F", "#FFE347", "#90BE6D", "#4D908E",
                                     "#43AA8B", "#006F57", "#277DA1", "#014F86"),
                       values = seq(0, 1, length.out = 15)) +
    geom_line(data = filter(population_data, 
                            `Indicator Name` == 'Population growth (annual %)'), 
              aes(y = Value * 10 + 90), color = "#FFC300", linewidth = 1, group = 1) +
    scale_y_continuous(sec.axis = sec_axis(~./10 - 9, 
                                           name = "Population Growth Rate (annual %)")) +
    labs(
      title = "Population and Population Growth Rate Over Time", 
      x = "Year", y = "Total Population (thousand)"
      ) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "none"
      )
```

### Demographic Composition

```{r}
# Create a demographic dataframe
composition_data <- data.frame(
  Group = c("Chuukese", "Pohnpeian", "Kosraean", "Yapese", 
            "Yap Outer Islands", "Asian", "Polynesian", "Other", "Unknown"),
  Percentage = c(48.8, 24.2, 6.2, 5.2, 4.5, 1.8, 1.5, 6.4, 1.4)
)

# Add a label with a percentage
composition_data$Label <- paste(composition_data$Group, "\n", 
                               round(composition_data$Percentage,2), "%", sep="")

# Draw a treemap and add labels
ggplot(composition_data, aes(area = Percentage, fill = Group, label = Label)) +
  geom_treemap(colour = "black", size = 1.5) +
  geom_treemap_text(colour = "white", place = "centre", grow = FALSE, reflow = TRUE) +
  labs(title = "Population Composition by Ethnolinguistic Group") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "none"
    ) +
  scale_fill_manual(values = c("#D00000", "#BB010B", "#F9844A", "#F9C74F", "#90BE6D",
                               "#43AA8B", "#277DA1", "#014F86", "#023E8A", "#03045E"))
```

### Male vs Female

```{r}
proportion_data <- long_data |> 
                   filter(`Indicator Name` %in% c('Population, female (% of total population)', 'Population, male (% of total population)'))

ggplot(proportion_data, aes(x = Year, y = Value , fill = `Indicator Name`)) +
    geom_bar(stat = "identity", position = "stack") +
    scale_fill_manual(values = c('Population, male (% of total population)' = '#003566',
                                 'Population, female (% of total population)' = '#D62828'),
                      name = "Gender", labels = c("Male Proportion", "Female Proportion")) +
    labs(
      title = "Male and Female Population Proportion",
      x = "Year", y = "Population Proportion (%)") +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1)
      )
```

### Life expectancy

```{r}
life_expectancy_data <- long_data |> 
                   filter(`Indicator Name` %in% 'Life expectancy at birth, total (years)')

ggplot(life_expectancy_data, aes(x = Year, y = Value)) +
  geom_line(color = "#0077B6", linewidth = 1) +
  geom_point(color = "#CD1624", size = 2) +
  labs(
    title = "Life Expectancy at Birth", 
    x = "Year", y = "Life Expectancy (Years)"
    ) +
  theme_minimal() +
  theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1)
      )
```

## Comparison with Other Regional Island States

```{r}
# Create dataframe
country_data <- data.frame(
  Country = c("Micronesia, Fed. Sts.", "Marshall Islands", "Nauru", "Palau"),
  Population = c(114164, 41569, 12668, 18055),
  PopulationGrowth = c(0.9, -1.2, 1.2, 0.2),
  PopDensity = c(166.1, 331.2, 543.6, 39.5),
  NetMigration = c(-635.0, -1901, -66, 3),
  LifeExpectancy = c(71, 65, 64, 69),
  SexRatio = c(103.4, 104, 101.8, 106),
  SurfaceArea = c(702, 181, 21, 459),
  HumanDevelopmentIndex = c(0.628, 0.639, 0.72, 0.767),
  CapitalCity = c("Palikir", "Majuro", "Yaren", "Ngerulmud"),
  Currency = c("USD", "USD", "AUD", "USD")
)

# Use gt to generate a table
gt_table <- gt(data = country_data) |> 
  tab_header(
    title = "Regional Island States: A Comparison of Social Indicators"
  ) |> 
  cols_label(
    Country = "Country",
    Population = "Population (2022)",
    PopulationGrowth = "Population growth (annual %, 2022)",
    PopDensity = "Pop. density (per km^2, 2021)",
    NetMigration = "Net migration (2021)",
    LifeExpectancy = "Life Expectancy at Birth, Total (years, 2021)",
    SexRatio = "Sex ratio (male per 100 female, 2022)",
    SurfaceArea = "Surface Area (km^2)",
    HumanDevelopmentIndex = "Human Development Index (2021)",
    CapitalCity = "Capital City",
    Currency = "Currency"
  ) |> 
  # Adjust column
  cols_width(
    Country ~ px(170),
    Population ~ px(100),
    PopulationGrowth ~ px(170),
    PopDensity ~ px(170),
    NetMigration ~ px(110),
    LifeExpectancy ~ px(200),
    SexRatio ~ px(160),
    SurfaceArea ~ px(130),
    HumanDevelopmentIndex ~ px(170),
    CapitalCity ~ px(100),
    Currency ~ px(100)
  ) |> 
  tab_options(
    row.striping.include_table_body = TRUE
  ) |> 
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = everything())
  ) |> 
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_column_labels(columns = everything())
  )
gt_table
```

```{r}
flags <- c("flags/Federated_States_of_Micronesia.png", 
           "flags/Marshall_Islands.png", "flags/Nauru.png", "flags/Palau.png")
```

```{r}
# Create dataframe
countries <- c("Micronesia", "Marshall Islands", "Nauru", "Palau")
economy <- data.frame(
  Country = rep(countries, each=3),
  Year = rep(c("2010", "2015", "2021"), times=4),
  GDP = c(297, 316, 414, 168, 181, 237, 59, 104, 133, 183, 279, 280),
  GDP_Per_Capita = c(2885, 2906.5, 3640.4, 2986.1, 3159.2, 4038.2, 5924.8, 10050.4, 
                     12350.9, 10219.9, 15784, 15572.5),
  Exports = c(23, 40, 34, 17, 25, 23, 25, 61, 54, 12, 6, 7),
  Imports = c(168, 160, 189, 76, 84, 72, 23, 109, 140, 107, 150, 216)
)
```

```{r}
# GDP Comparison
plot1 <- ggplot(economy, aes(x=Country, y=GDP, fill=Year)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values = c("#D62828", "#F77F00", "#457B9D")) + 
  geom_text(aes(label=GDP), vjust=-0.3, position=position_dodge(width=0.9), size=3.5) + 
  labs(
    title = "GDP Comparison", 
    x = "", y = "GDP (million current US$)"
       ) +
  theme_minimal() +
  theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5)
      )

plot1
```

```{r}
# GDP Per Capita Comparison
plot2 <- ggplot(economy, aes(x=Country, y=GDP_Per_Capita, fill=Year)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values = c("#D62828", "#F77F00", "#457B9D")) + 
  geom_text(aes(label=GDP_Per_Capita), position=position_dodge(width=0.9), 
            vjust=0.5, hjust=1.2, size=3.5, angle=90, colour="white") +
  labs(
    title = "GDP Per Capita Comparison", 
    x = "", y = "GDP Per Capita (current US$)"
       ) +
  theme_minimal() +
  theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5)
      )

plot2
```

```{r}
# Imports Comparison
plot3 <- ggplot(economy, aes(x=Country, y=Imports, fill=Year)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values = c("#D62828", "#F77F00", "#457B9D")) + 
  geom_text(aes(label=Imports), vjust=-0.3, position=position_dodge(width=0.9), size=3.5) + 
  labs(
    title = "Imports Comparison", 
    x = "", y = "Imports (million current US$)"
       ) +
  theme_minimal() +
  theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5)
      )

plot3
```

```{r}
# Exports Comparison
plot4 <- ggplot(economy, aes(x=Country, y=Exports, fill=Year)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values = c("#D62828", "#F77F00", "#457B9D")) + 
  geom_text(aes(label=Exports), vjust=-0.3, position=position_dodge(width=0.9), size=3.5) + 
  labs(
    title = "Exports Comparison", 
    x = "", y = "Exports (million current US$)"
       ) +
  theme_minimal() +
  theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5)
      )

plot4
```

## SWOT Analysis

**Strengths:**

1.  Strategic Location: Situated in the Western Pacific Ocean, Micronesia's extensive exclusive economic zone offers significant marine resources.

2.  U.S. Support: The Compact of Free Association with the United States provides substantial financial aid and development support.

3.  Natural Resources: The primary economic sector is commercial fishing, with significant income from fishing rights sales and offshore corporate registrations for captive insurance.

4.  Low Debt Levels: FSM has a relatively low government debt-to-GDP ratio, indicating financial stability.

**Weaknesses:**

1.  Economic Dependence: Heavy reliance on U.S. funding and grants, with a need to diversify economic sources.

2.  Limited Foreign Investment: Restrictions on foreign ownership and challenges in registering businesses deter foreign direct investment.

3.  Weak Infrastructure: Poor infrastructure and high costs of imported goods and services hamper economic growth.

4.  Subsistence Economy: Apart from a few urban centers, most of the economy is subsistence-based, limiting commercial activity.

**Opportunities:**

1.  Economic Diversification: Opportunities to diversify the economy beyond fishing and government employment.

2.  Tourism Potential: Natural beauty and unique culture offer potential for eco-tourism development.

3.  Trust Fund Utilization: Transitioning to using proceeds from a trust fund developed from U.S. contributions for development.

**Threats:**

1.  Reduction in Compact Funding: The shift in Compact funding methodology in 2023 poses financial challenges.

2.  Political Instability: Lack of political parties and potential for instability could affect economic decisions.

3.  Environmental Risks: As an island nation, Micronesia faces significant risks from climate change and natural disasters.

## Reference
